\documentclass[11pt]{article}

% Use this when displaying a new command

\newcommand{\command}[1]{``\lstinline{#1}''}
\newcommand{\program}[1]{\lstinline{#1}}
\newcommand{\url}[1]{\lstinline{#1}}
\newcommand{\channel}[1]{\lstinline{#1}}
\newcommand{\option}[1]{``{#1}''}
\newcommand{\step}[1]{``{#1}''}

\usepackage{longtable}

\usepackage{pifont}
\newcommand{\checkmark}{\ding{51}}
\newcommand{\naughtmark}{\ding{55}}

\usepackage{listings}
\lstset{
  basicstyle=\small\ttfamily,
  columns=flexible,
  breaklines=true
}

% Define the headers and footers

\usepackage{fancyhdr}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}

\pagestyle{fancy}

\fancyhf{}
\rhead{Computer Science 600}
\lhead{Syllabus}
\rfoot{Page \thepage}
\lfoot{Fall 2017}

% Use elastic spacing around the headers

\usepackage{titlesec}
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcommand{\syllabustitle}[1]
{
  \begin{center}
    \begin{center}
      \bf
      CMPSC 600\\Senior Thesis I\\
      Fall 2017\\
      \medskip
    \end{center}
    \bf
    #1
  \end{center}
}

\begin{document}

\thispagestyle{empty}

\syllabustitle{Syllabus}

\vspace*{-.3in}
\subsection*{Course Instructors}

\begin{tabular}{c c}

\begin{minipage}{3.5in}
Dr.\ Oliver Bonham-Carter \\
\noindent Office Location: Alden Hall 104 \\
\noindent Email: \url{obonhamcarter@allegheny.edu} \\
\end{minipage} &

\begin{minipage}{3.5in}
Dr.\ Janyl Jumadinova\\
\noindent Office Location: Alden Hall 105 \\
\noindent Email: \url{jjumadinova@allegheny.edu} \\
\end{minipage} \\

\begin{minipage}{3.5in}
Dr.\ Gregory M.\ Kapfhammer\\
\noindent Office Location: Alden Hall 108 \\
\noindent Email: \url{gkapfham@allegheny.edu} \\
\end{minipage} &

\begin{minipage}{3.5in}
Dr.\ Aravind Mohan\\
\noindent Office Location: Alden Hall Room 106\\
\noindent Email: \url{amohan@allegheny.edu} \\
\end{minipage}

\end{tabular}
\vspace*{-.3in}

\subsection*{Instructors' Office Hours}

Please visit the web sites of the course instructors to view their office hours. Using the ``appointment slots''
feature of Google Calendar, you can select an available meeting time. After picking your time slot, the reserved meeting
will appear in both your Google Calendar and the instructor's.

\vspace*{-.1in}
\begin{itemize}
  \itemsep -.25em
  \item Oliver Bonham-Carter: \url{http://www.cs.allegheny.edu/sites/obonhamcarter/}
  \item Janyl Jumadinova: \url{http://www.cs.allegheny.edu/sites/jjumadinova/}
  \item Gregory M.\ Kapfhammer: \url{http://www.cs.allegheny.edu/sites/gkapfham/}
  \item Aravind Mohan \url{http://www.cs.allegheny.edu/sites/amohan/}
\end{itemize}

\vspace*{-.25in}
\subsection*{Course Communication}

Throughout the semester, students and faculty will use Slack to support course
communication. Whenever possible, students are also encouraged to post
appropriate questions to a channel in Slack, which is available at
\url{https://CMPSC600Fall2017.slack.com}. Moreover, all students are required
to use GitHub repositories to submit all of the deliverables for this course's
various projects.

\vspace*{-.1in}
\subsection*{Course Schedule}

Organized according to the calendar month during which an activity takes place
or a project is due, the following table outlines this course's schedule for the
entire academic semester. Some of these dates are approximate and, if the need
to do so presents itself, it is possible for the course instructors to modify
the proposed schedule and notify the class of any changes via email or Slack.
Unless it is otherwise noted that there is no class session (e.g., on October
24, which is the College's Gator Day), it is assumed that, even if there is a
course project due or a research task to complete, you will still attend a
research group meeting during the scheduled session for this course.

\begin{center}
\begin{longtable}{r|l}

\hline

August 29 & No class on the first day of the semester \\

\hline

September 5  & Release Project One: Title, Abstract, Readers       \\
September 7  & Submit Project One: Title, Abstract, Readers        \\
September 8  & First and Second Readers Assigned                   \\
September 11 & Register for CMPSC 600 with First Reader            \\
September 12 & Schedule Weekly Meeting Time With Your First Reader \\
September 13 & Release Project Two: Senior Thesis Proposal         \\
September 19 & Release Project Three: Status Update \\
September 26 & Discuss Thesis Proposal and Status Update \\

\hline

October 3  & Submit Project Three: Status Update                \\
October 10 & Fall Break --- No Class                            \\
October 17 & Discuss the Oral Defense of Senior Thesis Proposal \\
October 24 & Gator Day --- No Class                             \\
October 31 & Submit Project Two: Senior Thesis Proposal         \\
October 31 & Schedule Proposal Defense with Pauline Lanzine     \\

\hline

November 7  & Release Project Four: Senior Thesis Chapters     \\
November 14 & Get Technical Report Number from Pauline Lanzine \\
November 21 & Review Outlines of Senior Thesis Chapters        \\
November 28 & Review Rough Drafts of Senior Thesis Chapters    \\

\hline

December 5  & Review Final Drafts of Senior Thesis Chapters \\
December 12 & Submit Project Four: Senior Thesis Chapters   \\

\hline

November 1 -- November 30 & Oral Defense of Thesis Proposal          \\
November 6 -- November 10 & Register for CMPSC 610 with first reader \\

\hline

September through December & Meet with first reader on a regular basis          \\
September through December & Communicate with instructors and students in Slack \\

\hline

\end{longtable}
\end{center}

\vspace*{-.25in}

\noindent Please note that, unless evidence of extenuating circumstances is
presented in writing to all of the instructors, a student's grade in the course
will be reduced if the stated deadlines are not met. Students who have questions
or concerns about these deadlines should talk with their first reader.

\subsection*{Required Textbooks}

\noindent{\em On Being a Scientist: A Guide to Responsible Conduct in Research}
(Third Edition).  Committee on Science, Engineering, and Public Policy, National
Academy of Sciences, National Academy of Engineering, and Institute of Medicine.
ISBN: 0309119715, 82 pages, 2009.\\ (References to the textbook are abbreviated
as ``OBAS'').

\noindent{\em BUGS in Writing: A Guide to Debugging Your Prose} (Second
Edition). Lyn Dupr\'e.  Addison-Wesley Professional.  ISBN-10: 020137921X and
ISBN-13: 978-0201379211, 704 pages, 1998.\\ (References to the textbook are
abbreviated as ``BIW'').

\noindent{\em Writing for Computer Science} (Second Edition).  Justin Zobel.
Springer ISBN-10: 1852338024 and ISBN-13: 978-1852338022, 270 pages, 2004. \\
(References to the textbook are abbreviated as ``WFCS'').

\subsection*{Overview of the Grading Policies}

Final grades are determined after the entire faculty of the Department of
Computer Science --- not just your course instructor for CMPSC 600 --- review
and discuss all of the submitted deliverables.

Your grade in CMPSC 600 will be based on a combination of the following
activities and deliverables. Percentages are not given because we recognize that
the senior thesis experience differs from one student to the next and that there
are many variables, such as the nature of the project and the availability of
external resources, that can influence the relative importance of these
criteria. However, it is important to note that a large percentage of your grade
depends upon your written thesis proposal, the oral defense of your thesis
proposal, and your two thesis chapters.

\begin{itemize}
  \itemsep -.25em

  \item {\bf Class Participation}: This includes meeting regularly with your
    first reader. Although the exact details about frequency and length of each
    meeting must be established with your first reader, you should adhere to the
    previously stated schedule. Additionally, this also requires regular
    contributions, in the form of questions and comments, to the course's Slack
    team. As previously mentioned in the ``Course Schedule'' section, all
    students are required to attend all of the Tuesday class sessions and to
    fully participate in their research group meetings.

  \item {\bf Course Repositories}: This involves students creating, at minimum,
    a GitHub version control repository for each of the assigned course
    projects. Students should click the relevant link in the Slack team to
    accept and begin working on the assignment. Now, you may follow the
    instructions in your repository's README file to complete and submit the
    assignment, regularly using the Travis system and GitHub's tagging mechanism
    to release PDFs of your proposal with versions that adhere to the semantic
    versioning standard. Course instructors will only grade and provide feedback
    on projects that are stored and released through GitHub.

  \item {\bf Status Update}: This document should describe the progress that a
    student has made on identifying a topic for their senior thesis and
    completing the preliminary research needed to demonstrate its feasibility.
    Written with feedback from your first and second readers, your status update
    should be stored and released through the appropriate GitHub repository.

  \item {\bf Written Proposal}: This document must be submitted, through the
    appropriate GitHub repository, to both your first and second reader. Subject
    to multiple rounds of extensive revision, this technical document must be
    formatted according to the Department's thesis proposal style requirements
    and approved for a subsequent defense by your first reader.

  \item {\bf Proposal Defense}: This event is scheduled in consultation with
    your first and second reader and the building coordinator, Pauline Lanzine.
    Students may not schedule their proposal defense until their thesis proposal
    has been formally approved, after multiple rounds of revision, by their
    first reader. Evidence of this approval must be submitted to Pauline Lanzine
    when scheduling your defense. In particular, your first reader must place a
    note in your proposal's GitHub commit log to indicate that your proposal is
    approved for an oral defense.

  \item {\bf Thesis Chapters}: Any two chapters of your final senior thesis must
    be submitted to the course instructor by the aforementioned deadline.
    Written in a professional and scientific style, these chapters must be
    formatted in the department's thesis style; note that this style, which is
    different from the proposal style, is available from an appropriate GitHub
    repository.

\end{itemize}

\subsection*{Details About Course Expectations and Deliverables}

\subsubsection*{Class Participation}

Once your readers have been assigned, you must regularly meet with your first
reader, who will report on your participation when the department's faculty meet
to assign final grades.  Students are expected to come to each meeting with a
status update on their progress and a meeting agenda.  Students should conclude
each meeting by listing the tasks that they want to complete before the next
meeting. In addition, students should regularly participate in the discussions
on the relevant channels in the Slack team for our course. Your participation on
Slack may involve giving a quick status update to your first reader, inviting
your first reader to examine a draft of your proposal or compile and run a new
version of a program, or, within the bounds of the Honor Code, answering a
question from another senior conducting their thesis research.  Finally, all
students are required to attend and actively participate in all of the class
sessions that will involve both meetings with their research group and informal
discussion during the departmental coffee and tea session. Evidence of regular
participation must be submitted to the course instructor; failure to participate
and submit this evidence will result in the reduction of your grade in CMPSC
600.

\subsubsection*{GitHub Repositories}

Every student must accept each of course projects, thereby creating a GitHub
repository customized for the student and that specific project. All of these
GitHub repositories should have a README file that clearly explains the steps
that a student took to complete and release the final version of the assignment.
In addition to containing the \LaTeX{} source code that fulfills the assignment,
each GitHub repository should feature releases of the compiled PDF files that
are tagged with numbers that adhere to the semantic versioning standard
described at \url{http://semver.org/}. The release of a compiled PDF file can be
accomplished automatically by using both the tagging and releases feature
provided by GitHub and, additionally, the continuous integration system provided
by Travis. Your first and second readers will download, read, and comment on a
released PDF at semantic version 1.0.0 or higher. Students who are not able to
automatically release PDFs of their projects may instead manually create them by
using the GitHub interface. Please see an instructor if you have questions about
using GitHub. Failure to either regularly commit to your GitHub repositories or
to make releases of your PDFs will lead to a decrease in your final grade for
CMPSC 600.

\subsubsection*{Thesis Proposal}

The proposal should follow the Department's proposal style and thus must include
an abstract, the main body of your proposal, a tentative schedule for completing
the project, a bibliography, and any other information deemed important by your
first reader. These other details will often include one or more of the
following: a survey of the existing literature; an overview of your proposed
technique; technical diagrams and formal statements of algorithms illustrating
your main approach; the description of an evaluation method; examples or code
artifacts or other evidence that you understand the nature of the work you are
proposing and can feasibly complete it in the time available.  Finally, the
proposal must fully adhere to professional standards of writing.

Although your first reader will be your primary contact person as your write and
revise your thesis proposal, you may involve your second reader as appropriate.
That is, your first reader will make suggestions on your submitted drafts under
the expectation that you will revise multiple proposal drafts. You must work at
a pace that will ensure that you complete an approved senior thesis proposal
before the stated deadline. Failure to complete a final thesis proposal and
secure formal approval of your proposal before this date will result in the
reduction of your final grade in CMPSC 600. Securing formal approval of your
thesis involves a student having their first reader note in the GitHub commit
log that the final version of the thesis proposal is suitable for a senior
thesis defense. This evidence must be shown to both a course instructor and
Pauline Lanzine when scheduling your proposal defense; no defense will be
scheduled without this evidence of approval.

\subsubsection*{Proposal Defense}

Last approximately one hour in total, a proposal defense starts with a prepared,
formal presentation of about ten minutes in which you lay out the essential
parts of your chosen project under the assumption that your first and second
reader have already studied your thesis proposal. Following the presentation
that is supported by polished slides, you will participate in a discussion with
your readers to identify potential challenges, refine or modify some aspects of
the thesis proposal, and ensure that your project is feasible and appropriate.
All components of your proposal defense should be completed in consultation with
your first and second readers. You must schedule your proposal defense during
the stated course session. Your grade in CMPSC 600 will be reduced if you miss
the deadline for scheduling or conducting the defense of your thesis proposal.

\subsubsection*{Thesis Chapters}

Your two chapters, due on the previously stated date, should represent a
significant addition to or extension of the material in your proposal. Don't
simply ``split the proposal into two chapters'' --- this usually does not work
well since your chapters must represent work completed, not work being proposed.
Chapters are judged according to the same professional standards as the
proposal; they must include a full bibliography, a preliminary table of
contents, lists of any figures and tables, and any other items (e.g., the formal
statement of key algorithms) required by your first reader.

As you write your chapters in consultation with your readers, allow these
individuals to comment on your drafts and then make all of their requested
changes. You will also be given the opportunity to plan and revise your thesis
chapters during certain meetings of your research group. You should plan to
write several drafts of the chapters before submitting them on the due date;
failure to turn them by the stated deadline will result in the reduction of your
final grade in CMPSC 600.

% \subsubsection*{Seeking Assistance}

% Students who are struggling to understand the knowledge and skills developed in a class or laboratory session are
% encourage to seek assistance from the course instructor. Throughout the semester, students should, within the bounds of
% the Honor Code, ask and answer questions on the Slack site for our course; please request assistance from the instructor
% first through Slack before sending an email. Students who need the course instructor's assistance must schedule a
% meeting through his web site and come to the meeting with all of the details needed to discuss their question.

\subsubsection*{Using Email}

Although we will primarily use Slack for class communication, we will sometimes
use email to send announcements about important class matters. It is your
responsibility to check your email at least once a day and to ensure that you
can reliably send and receive emails. This class policy is based on the
statement about the use of email that appears in {\em The Compass}, the student
handbook.

\subsection*{Honor Code}

The Academic Honor Program that governs the academic program at Allegheny
College is described in the Allegheny Academic Bulletin. The Honor Program
applies to all work that is submitted for academic credit or to meet non-credit
requirements for graduation at Allegheny College. This includes all work
assigned for these classes (e.g., source code, technical diagrams, and your
written content); deliverables that are nearly identical the work of others will
be taken as evidence of violating the Honor Code. All students who have enrolled
in the College will work under the Honor Program. Each student who has
matriculated at the College has acknowledged the following pledge:

\begin{quote}
I hereby recognize and pledge to fulfill my responsibilities, as defined in the Honor Code, and to maintain the
integrity of both myself and the College community as a whole.
\end{quote}

\subsection*{Disability Services}

The Americans with Disabilities Act (ADA) is a federal anti-discrimination
statute that provides comprehensive civil rights protection for persons with
disabilities.  Among other things, this legislation requires all students with
disabilities be guaranteed a learning environment that provides for reasonable
accommodation of their disabilities. Students with disabilities who believe they
may need accommodations in this class are encouraged to contact Disability
Services at 332--2898.  Disability Services is part of the Learning Commons and
is located in Pelletier Library. Please do this as soon as possible to ensure
that approved accommodations are implemented in a timely fashion.

\subsection*{Welcome to an Adventure in Computer Science}

CMPSC 600 affords you the opportunity to pursue independent research in computer
science and to ensure that your work has a positive influence on your future
plans, the students and faculty at Allegheny College, and a broader society that
relies heavily on computer hardware and software.  At the start of your senior
year, we invite you to pursue this class with great enthusiasm and vigor.

\end{document}
